Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-26 docs/papers/roofline_model/gocean_roofline.tex
roofline: update of stream2 results on desktop

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2} we plot the
results obtained from the DAXPY component of the STREAM2 benchmark on
both of the CPUs examined here. The plateaux in bandwidth for L2, L3
and main memory are clear but that for L1 is considerably noisier. The
final values we have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}.

\begin{figure}
\includegraphics{stream2_desktop}
\includegraphics{stream2_archer}
\caption{Results from running the STREAM2 benchmark on the E5-1620
  (top) and E5-2697 (bottom) CPUs.}
\label{FIG_stream2}
\end{figure}

>>>>

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2} we plot the
results obtained from the DAXPY component of the STREAM2 benchmark on
both of the CPUs examined here. The plateaux in bandwidth for L2, L3
and main memory are clear but that for L1 is considerably noisier. The
final values we have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}. On the E5-1620 the benchmark was
compiled with the Intel v.16 compiler with the flags ``-O3
-fast''. Strangely, we found that dropping ``-fast'' from the link
stage resulted in better bandwidth to main memory. Removing ``-fast''
altogether and just using ``-O3 -xHost'' gave identical results.

\begin{figure}
\includegraphics{stream2_desktop}
\includegraphics{stream2_archer}
\caption{Results from running the STREAM2 benchmark on the E5-1620
  (top) and E5-2697 (bottom) CPUs. Error bars indicate the maximum and
  minimum values obtained from 200 runs performed for each array
  size. }
\label{FIG_stream2}
\end{figure}

The bandwidths obtained on the E5-1620 are significantly greater than
those on the E5-2697.  {\bf need to check by re-running on Archer with
  200 repeats and new min/max results}.
